Optimal (Multiway) Spatial Joins

### 2024-06-04 msj.tex

\noindent To prove the above, we must explain why $r$ contains the effective horizontal segment of $\bm{t}$. Since $r \in \contained_{R_{k-2}}(h^*)$, we know that $r$ covers the segment $[x_1, \minleft(h')] \times y$. Hence, $[x_1, \minleft(h')]$ $\subseteq [\xleft(r), \xright(r)]$ and $y \in [\ybot(r), \ytop(r)]$.
Using also the condition $\xright(r) \ge x$ given in claim 2, we can derive $[x_1, x] \subseteq [\xleft(r), \xright(r)]$. Therefore, $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$, is contained in $r$.

>>>>

\noindent To prove the above, we must explain why the rectangle $r$ in the claim contains the effective horizontal segment of $\bm{t}$. Since $r \in \contained_{R_{k-2}}(h^*)$, we know that $r$ covers the segment $[x_1, \minleft(h')] \times y$. Hence, $[x_1, \minleft(h')]$ $\subseteq [\xleft(r), \xright(r)]$ and $y \in [\ybot(r), \ytop(r)]$. Using also the condition $\xright(r) \ge x$ given in claim 2, we can derive $[x_1, x] \subseteq [\xleft(r), \xright(r)]$. Therefore, $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$, is contained in $r$, establishing claim 2.
